Supporting Information : Effect of copula on extinction risk

### 2019-02-27 SuppMat.Rmd
adding figures...continued

```{r fig_ricker_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_ricker_local,res_ricker_global)}
pdf(paste(resloc,"ricker_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
#op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))

  #---------------------------------------------------
  ## Allow a second plot on the same graph
  #par(new=TRUE)

@@

pdf(paste(resloc,"ricker_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

@@

pdf(paste(resloc,"ricker_extrisk_d0.pdf",sep=""),height=6,width=6)

plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_left_d0,col="red",type="b",
     ylim=c(0,1),xlim = range(ricker_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025left,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975left,
       angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted") #rc=1

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025right,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(0.2,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)

dev.off()
```

@@

```{r fig_hassell_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_hassell_local,res_hassell_global)}
pdf(paste(resloc,"hassell_ext_risk_local_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

pdf(paste(resloc,"hassell_ext_risk_global_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5.2,4.2,1.2,1.5))

@@

pdf(paste(resloc,"hassell_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted")

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025right,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(2,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)

dev.off()
```

@@

```{r fig_msmith_scl_0.8, echo=F, results="hide",cache=T, cache.extra=list(seed,res_msmith_local,res_msmith_global)}
pdf(paste(resloc,"msmith_ext_risk_local_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5.2,4.2,1.2,1.5))

@@

pdf(paste(resloc,"msmith_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(msmith_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_msmith,lty="dotted")

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025right,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(1.2,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
dev.off()
```

@@

```{r fig_pennycuick_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_pennycuick_local,res_pennycuick_global)}
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5.2,4.2,1.2,1.5))

@@

pdf(paste(resloc,"pennycuick_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(pennycuick_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025left,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted")

lines(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025right,x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(3,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)

dev.off()
```

@@

```{r fig_verhulst_scl_0.6, echo=F, results="hide",cache=T, cache.extra=list(seed,res_verhulst_local,res_verhulst_global)}
pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

pdf(paste(resloc,"verhulst_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

pdf(paste(resloc,"verhulst_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(verhulst_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025left,x1=verhulst_extrisk_d0$r,
       y1=verhulst_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_verhulst,lty="dotted")

lines(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025right,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(0.4,0.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
dev.off()
```

@@

```{r fig_abrewer_scl_0.6, echo=F, results="hide",cache=T, cache.extra=list(seed,res_abrewer_local,res_abrewer_global)}
pdf(paste(resloc,"abrewer_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

pdf(paste(resloc,"abrewer_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

abrewer_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims
abrewer_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims
abrewer_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims
abrewer_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims
pdf(paste(resloc,"abrewer_extrisk_d0.pdf",sep=""),height=6,width=6)
plot(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(abrewer_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025left,x1=abrewer_extrisk_d0$r,
       y1=abrewer_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_abrewer,lty="dotted")

lines(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025right,
       x1=abrewer_extrisk_d0$r,y1=abrewer_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(0.005,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)
dev.off()
```

<!--Ricker model-->
![Effect of non-Normal environmental noise copula on extinction risk after 25 years; Ricker model with local dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_local_disp_scl_1}](./Results/ricker_scl_1/ricker_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years ; Ricker model with global dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_global_disp_scl_1}](./Results/ricker_scl_1/ricker_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (ricker model with no dispersion : rc=1); numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_d0_scl_1}](./Results/ricker_scl_1/ricker_extrisk_d0.pdf){ width=40%, height=40% }

>>>>

```{r fig_ricker_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_ricker_local,res_ricker_global)}

pdf("./Results/common_legend.pdf",height=1,width=12)
op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0))
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("center", c("noise : LTdep.","noise : RTdep."), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'),x.intersp = 0.2,
         cex = 2.5, xpd = TRUE, horiz = T, inset = c(0,0), 
         bty = "n")
par(op)
dev.off()

pdf(paste(resloc,"ricker_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
#op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
  #---------------------------------------------------
  ## Allow a second plot on the same graph
  #par(new=TRUE)

@@

pdf(paste(resloc,"ricker_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

pdf(paste(resloc,"ricker_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_left_d0,col="red",type="b",
     ylim=c(0,1),xlim = range(ricker_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025left,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975left,
       angle=90,length=0.1,col="red",code=3)
abline(v=rc_ricker,lty="dotted") #rc=1

lines(ricker_extrisk_d0$r,ricker_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=ricker_extrisk_d0$r,y0=ricker_extrisk_d0$CI0.025right,x1=ricker_extrisk_d0$r,y1=ricker_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("bottomright", c("Ricker",paste0("K = ",K),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
#legend("bottomright", c("noise : LTdep.","noise : RTdep."), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=F, bty='n',cex=1.5)
par(op)
dev.off()
```

@@

```{r fig_hassell_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_hassell_local,res_hassell_global)}
pdf(paste(resloc,"hassell_ext_risk_local_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"hassell_ext_risk_global_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

pdf(paste(resloc,"hassell_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(hassell_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted")

lines(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025right,x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("bottomright", c("Hassell",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

```{r fig_msmith_scl_0.8, echo=F, results="hide",cache=T, cache.extra=list(seed,res_msmith_local,res_msmith_global)}
pdf(paste(resloc,"msmith_ext_risk_local_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5))

@@

pdf(paste(resloc,"msmith_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(msmith_extrisk_d0$r),
     xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,
       x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_msmith,lty="dotted")

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025right,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("bottomright", c("Maynard Smith",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

```{r fig_pennycuick_scl_1, echo=F, results="hide",cache=T, cache.extra=list(seed,res_pennycuick_local,res_pennycuick_global)}
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.2,1.5),mgp=c(2,0.5,0))

@@

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=12,width=12)
op<-par(mfrow=c(4,4),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

pdf(paste(resloc,"pennycuick_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(pennycuick_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025left,
       x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_pennycuick,lty="dotted")

lines(pennycuick_extrisk_d0$r,pennycuick_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=pennycuick_extrisk_d0$r,y0=pennycuick_extrisk_d0$CI0.025right,x1=pennycuick_extrisk_d0$r,y1=pennycuick_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("bottomright", c("Pennycuick",paste0("a = ",a," ,b = ",b),paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

```{r fig_verhulst_scl_0.6, echo=F, results="hide",cache=T, cache.extra=list(seed,res_verhulst_local,res_verhulst_global)}
pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"verhulst_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

pdf(paste(resloc,"verhulst_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(verhulst_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025left,x1=verhulst_extrisk_d0$r,
       y1=verhulst_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_verhulst,lty="dotted")

lines(verhulst_extrisk_d0$r,verhulst_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=verhulst_extrisk_d0$r,y0=verhulst_extrisk_d0$CI0.025right,
       x1=verhulst_extrisk_d0$r,y1=verhulst_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("bottomright", c("Verhulst",paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

@@

```{r fig_abrewer_scl_0.6, echo=F, results="hide",cache=T, cache.extra=list(seed,res_abrewer_local,res_abrewer_global)}
pdf(paste(resloc,"abrewer_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

pdf(paste(resloc,"abrewer_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5,4,1.5,1.5),mgp=c(2,0.5,0))

@@

abrewer_extrisk_d0$CI0.025left<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims
abrewer_extrisk_d0$CI0.975left<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_left_d0)/numsims
abrewer_extrisk_d0$CI0.025right<-qbinom(p=0.025,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims
abrewer_extrisk_d0$CI0.975right<-qbinom(p=0.975,size=numsims,prob=abrewer_extrisk_d0$risk_right_d0)/numsims
pdf(paste(resloc,"abrewer_extrisk_d0.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),
     xlim = range(abrewer_extrisk_d0$r),xlab="r",ylab="Extinction risk",cex.lab=2,cex.axis=1.5,pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025left,x1=abrewer_extrisk_d0$r,
       y1=abrewer_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_abrewer,lty="dotted")

lines(abrewer_extrisk_d0$r,abrewer_extrisk_d0$risk_right_d0,col="blue",type="b",pch=1)
arrows(x0=abrewer_extrisk_d0$r,y0=abrewer_extrisk_d0$CI0.025right,
       x1=abrewer_extrisk_d0$r,y1=abrewer_extrisk_d0$CI0.975right,angle=90,length=0.1,col="blue",code=3)
legend("bottomright", c("Austin-Brewer",paste0("sd =",scl)), horiz=F, bty='n',cex=1.8)
par(op)
dev.off()
```

<!--Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp.pdf}\\
\caption{Effect of non-Normal environmental noise copula on extinction risk after 25 years; Ricker model with local dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--Ricker model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_global_disp.pdf}\\
\caption{Effect of non-Normal environmental noise copula on extinction risk after 25 years; Ricker model with global dispersion; numlocs=5, numsteps=25, numsims=10000, scl=1 \label{fig_ricker_risk_global_disp_scl_1}}
\end{center}
\end{figure}
